Target Speaker Extraction using Discrete Representations from Self-Supervised Models and Language Models \thanks{Identify applicable funding agency here. If none, delete this.}

### 2024-09-06 src/paper.tex
update

\begin{table*}
    \setlength{\tabcolsep}{12pt} % Adjust column spacing
    \renewcommand{\arraystretch}{1.3}
    \begin{center}
        \begin{tabular}{ccccccccc}
            \Xhline{2\arrayrulewidth} % Bold top line
            \multirow{2}{*}{System} & \multirow{2}{*}{Category} & \multirow{2}{*}{Model type} & \multirow{2}{*}{Model size} & \multicolumn{3}{c}{ DNSMOS $\uparrow$} & \multirow{2}{*}{dWER $\downarrow$} & \multirow{2}{*}{Spk Sim $\uparrow$} \\
            \cline{5-7}
              &                   &                             &                             & SIG     & BAK     & OVL    &                       &                          \\ 
            \hline
            Mixture                 & - & -                           & -                           & 3.39    & 3.14    & 2.68   & 79.3\%                & -                        \\
            Target-discrete-WavLM   & G & -                          & 330M                           & 3.57    & 4.10    & 3.32   & 11.3\%                & 0.653                    \\
            \hline
            Spex+                   &  D & Continuous                  & 11M                         & 3.36    & 3.76    & 2.98   & 19.3\%                & 0.923                    \\
            \hline
            Continuous-WavLM   & G    & Continuous                  & 220M                        & 3.56    & 4.06    & 3.27   & 14.7\%                & 0.877                    \\
            TSELM-L-Hybrid    & G       & Hybrid                      & 468M                        & 3.50    & 4.06    & 3.22   & 19.8\%                & 0.924\_d                 \\
            TSELM-S-NoConcat           & G       & Discrete                    & 354M                        & 3.47    & 4.03    & 3.19   & 69.6\%                & 0.868\_d                 \\
            \hline
            TSELM-S           & G       & Discrete                    & 354M                        & 3.50    & 4.07    & 3.24   & 28.1\%                & 0.892\_d                 \\
            TSELM-M          & G        & Discrete                    & 389M                        & 3.49    & 4.05    & 3.22   & 28.4\%                & 0.901\_d                 \\
            TSELM-L         & G         & Discrete                    & 468M                        & 3.49    & 4.05    & 3.22   & 27.1\%                & 0.905\_d \\
            \Xhline{2\arrayrulewidth} % Bold top line              
            \end{tabular}
            \linebreak
            \caption{The performance of different systems on Libri2Mix testset. For TSELM-L-Hybrid  
            and TSELM, we compare the speaker similarity with the discretized target speech 
            (Target-discrete-WavLM) instead of the target speech due to the observation that 
            the process of discretization already losses the speaker information (0.653 for 
            Target-discrete-WavLM). We use "\_d" to denote it.  }
            \label{main_exp}
      \end{center}
  \end{table*}

@@

@@

>>>>

\begin{table*}
    \caption{The performance of different systems on Libri2Mix testset. For TSELM-L-Hybrid  
    and TSELM, we compare the speaker similarity with the discretized target speech 
    (Target-discrete-WavLM) instead of the target speech due to the observation that 
    the process of discretization already losses the speaker information (0.653 for 
    Target-discrete-WavLM). We use "\_d" to denote it.  }
    \setlength{\tabcolsep}{12pt} % Adjust column spacing
    \renewcommand{\arraystretch}{1.3}
    \begin{center}
        \begin{tabular}{ccccccccc}
            \Xhline{2\arrayrulewidth} % Bold top line
            \multirow{2}{*}{System} & \multirow{2}{*}{Category} & \multirow{2}{*}{Model type} & \multirow{2}{*}{Model size} & \multicolumn{3}{c}{ DNSMOS $\uparrow$} & \multirow{2}{*}{dWER $\downarrow$} & \multirow{2}{*}{Spk Sim $\uparrow$} \\
            \cline{5-7}
              &                   &                             &                             & SIG     & BAK     & OVL    &                       &                          \\ 
            \hline
            Mixture                 & - & -                           & -                           & 3.39    & 3.14    & 2.68   & 79.3\%                & -                        \\
            Target-discrete-WavLM   & G & -                          & 330M                           & 3.57    & 4.10    & 3.32   & 11.3\%                & 0.653                    \\
            \hline
            Spex+                   &  D & Continuous                  & 11M                         & 3.36    & 3.76    & 2.98   & 19.3\%                & 0.923                    \\
            \hline
            Continuous-WavLM-L6   & G    & Continuous                  & 220M                        & 3.56    & 4.06    & 3.27   & 14.7\%                & 0.877                    \\
            TSELM-L-Hybrid    & G       & Hybrid                      & 468M                        & 3.50    & 4.06    & 3.22   & 19.8\%                & 0.924\_d                 \\
            TSELM-S-NoConcat           & G       & Discrete                    & 354M                        & 3.47    & 4.03    & 3.19   & 69.6\%                & 0.868\_d                 \\
            \hline
            TSELM-S           & G       & Discrete                    & 354M                        & 3.50    & 4.07    & 3.24   & 28.1\%                & 0.892\_d                 \\
            TSELM-M          & G        & Discrete                    & 389M                        & 3.49    & 4.05    & 3.22   & 28.4\%                & 0.901\_d                 \\
            TSELM-L         & G         & Discrete                    & 468M                        & 3.49    & 4.05    & 3.22   & 27.1\%                & 0.905\_d \\
            \Xhline{2\arrayrulewidth} % Bold top line              
            \end{tabular}
            \linebreak
            \label{main_exp}
      \end{center}
    %   \vspace{-10pt}
  \end{table*}

@@

\begin{table}

    \renewcommand{\arraystretch}{1.2}
    \begin{center}
        \begin{tabular}{ccccccc}
            \Xhline{2\arrayrulewidth} % Bold top line
            \multirow{2}{*}{SSL-Model} & \multirow{2}{*}{Type} & \multicolumn{3}{c}{ DNSMOS $\uparrow$} & \multirow{2}{*}{dWER $\downarrow$} & \multirow{2}{*}{Spk Sim $\uparrow$} \\
            \cline{3-5}
                                                       &                             & SIG     & BAK     & OVL    &                       &                          \\ 
            \hline
            \multirow{2}{*}{Hubert}                              &  Discrete                          & 3.56    & 4.09    & 3.30   & 81.3\%                & 0.865\_d                        \\
                                             &  Hybrid                          & 3.57    & 4.10    & 3.32   & 35.1\%                & 0.907\_d                        \\
            \hline
            \multirow{2}{*}{WavLM-L6}                              &  Discrete                          & 2.08    & 2.07    & 1.64   & 122.1\%                & 0.589\_d                        \\
            &  Hybrid                          & 3.54    & 3.84    & 3.12   & 30.0\%                & 0.849\_d                        \\
            \hline
            \hline
            \multirow{2}{*}{WavLM}                                     &  Discrete                          & 3.49    & 4.05    & 3.22   & 27.1\%                & 0.905\_d                        \\
                                              &  Hybrid                          & 3.50    & 4.06    & 3.22   & 19.8\%                & 0.924\_d                        \\

            \Xhline{2\arrayrulewidth} % Bold top line              
            \end{tabular}
            \label{abla_1}

      \end{center}
      \caption{Iwdad}
      \vspace{-25pt}
    \end{table}

@@

\section{Conclusion}
